---
title: "The Perks of Writing Functions"
subtitle: "" 
author: "Antoine Languillaume"
date: "2021/05/07"
output:
  xaringan::moon_reader:
    css: [xaringan-themer.css, style.css]
    lib_dir: libs
    nature:
      # highlightStyle: solarized-dark
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  base_color = "#3C989E",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

---
class: inverse, center, middle

# Before Anything: Launch Binder

---

--

### Everybody uses functions

```{r, tidy=FALSE}
x <- c(4, 2, 4, 6)
mean(x)
```

--

### Because nobody will find that useful

```{r eval=FALSE, tidy=FALSE}
(4 + 2 + 4 + 6) / 4
```

---

## Functions are:

```{r, tidy=FALSE}
mean(x)
```

.list[
* Software atoms

* Recipes for a given computation

* Take arguments and return result
]

---
class: inverse, center, middle

# Anatomy of a Function

---

.function[
.dimmed[.focus[name] <- function(arg_1, arg_2 = "default_value") {

 

return(result)

}
]
]

.function_components[
.dimmed[
.focus[meaningful name]

function key word

arguments

body

optional return statement
]
]


---

.function[
.dimmed[
name <- .focus[function](arg_1, arg_2 = "default_value") {

  .# body

return(result)

}
]
]

.function_components[
.dimmed[
meaningful name

.focus[function key word]

arguments

body

optional return statement
]
]

---

.function[
.dimmed[
name <- function(.focus[arg_1, arg_2 = "default_value"]) {

  .# body

return(result)

}
]
]

.function_components[
.dimmed[
meaningful name

function key word

.focus[arguments]

body

optional return statement
]
]

---

.function[
.dimmed[
name <- function(arg_1, arg_2 = "default_value") {

  .focus[.# body]

return(result)

}
]
]

.function_components[
.dimmed[
meaningful name

function key word

arguments

.focus[body]

optional return statement
]
]

---

.function[
.dimmed[
name <- function(arg_1, arg_2 = "default_value") {
]

 temp_var <- do_something(arg_1)

full_results <- combine_stuff(temp_var, arg_2)

result <- full_results["important_part"]
  
.dimmed[
return(result)

}]
]


.function_components[
.dimmed[
meaningful name

function key word

arguments

.focus[body]

optional return statement
]
]




---

.function[
.dimmed[
name <- function(arg_1, arg_2 = "default_value") {

  .# body

  .focus[return(result)]

}
]
]

.function_components[
.dimmed[
meaningful name

function key word

arguments

body

.focus[optional return statement]
]
]

---
class: inverse, center, middle

# Let's code !

---
class: inverse, center, middle

# DRY

---

class: inverse, center, middle

# Documentation

---

# Wrap up

.list[
* Basic Anatomy (name, arguments, body, output)

* Capture pattern (DRY)

* Can be documented (Roxygen2 syntax)

* Building blocks of efficient code
]

---

class: inverse, center, middle

# Thanks a lot and keep coding !

---